\documentclass[authoryear]{elsarticle}

\usepackage{fullpage}
\usepackage[labelfont=bf,labelsep=newline,singlelinecheck=false,aboveskip=0pt]{caption}
\DeclareCaptionFormat{myformat}{#1#2\\#3}
\usepackage{amsmath,graphicx,subfigure,multicol,chngpage,setspace}
\usepackage[colorlinks=true,linkcolor=black, citecolor=blue, urlcolor=blue]{hyperref}
\linespread{1.3}
\usepackage[top=1in, bottom=1in, left=1.2in, right=1.2in]{geometry}
\usepackage[usenames,dvipsnames]{pstricks}
\usepackage{epsfig}
\usepackage{pst-func}
\usepackage{lineno}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{lscape}
\usepackage{rotating}
\usepackage{epstopdf}
\modulolinenumbers[5]

\begin{document}
\begin{frontmatter}

\title{Working Title: Structural Breaks and Machine Learning}


\author[a]{Yamin Ahmad}
\ead{ahmady@uww.edu}
\author[b]{Adam Check}
\ead{ajc@stthomas.edu}
\author[c]{Ming Chien Lo}
\ead{Ming Lo <Ming.Lo@metrostate.edu>}


\address[a]{University of Wisconsin - Whitewater, Department of Economics, Hyland Hall, 800 W. Main St, Whitewater WI 53190, USA}
\address[b]{University of St. Thomas, Dept. of Economics, Mail 5029, 2115 Summit Avenue, St. Paul, MN 55105, USA}
\address[c]{Metropolitan State University, Department of Economics and Finance, 1501 Hennepin Avenue, Minneapolis, MN 55403, USA }



\begin{abstract}
This paper examines identification of structural breaks using Machine Learning.
\end{abstract}

\end{frontmatter}

[THIS IS A PRELIMINARY DRAFT. PLEASE DO NOT CITE OR DISTRIBUTE WITHOUT THE PERMISSION OF THE AUTHORS.]

\section{Introduction}
Intro goes here

\section{Model}
Outline model here.


\section{Methodology and Analyses}
Methodology goes here

\section{Results}
Results go here

\section{Conclusion}
Concluding remarks to be added later.

\section*{Acknowledgements}
We thank the following institutions and people for research support. All errors are our own.


\section*{References}
References go here


\end{document}
